---
output: rmarkdown::github_document
---

# vershist

Collect Version Histories For Vendor Products

## Description

Provides a set of functions to gather version histories of products 
(mainly software products) from their sources (generally websites).

## What's Inside The Tin

The following functions are implemented:

Core:

- `apache_httpd_version_history`:	Retrieve Apache httpd Version Release History
- `lighttpd_version_history`:	Retrieve lighttpd Version Release History
- `memcached_version_history`:	Retrieve memcached Version Release History
- `mongodb_version_history`:	Retrieve MongoDB Version Release History
- `mysql_version_history`:	Retrieve MySQL Version Release History
- `nginx_version_history`:	Retrieve nginx Version Release History
- `openresty_version_history`:	Retrieve openresty Version Release History
- `openssh_version_history`:	Retrieve OpenSSH Version Release History
- `sendmail_version_history`:	Retrieve sendmail Version Release History
- `sqlite_version_history`:	Retrieve sqlite Version Release History

Utility:

- `is_valid`:	Test if semantic version strings are valid

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/vershist")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(vershist)

# current verison
packageVersion("vershist")
```

Apache

```{r apache, cache=TRUE}
apache_httpd_version_history()
```

lighttpd

```{r lighttpd, cache=TRUE}
lighttpd_version_history()
```

memcached

```{r memcached, cache=TRUE}
memcached_version_history()
```

mongodb

```{r mongodb, cache=TRUE}
mongodb_version_history()
```

MySQL

```{r mysql, cache=TRUE}
mysql_version_history()
```

nginx

```{r nginx, cache=TRUE}
nginx_version_history()
```

openresty

```{r openresty, cache=TRUE}
openresty_version_history()
```

OpenSSH

```{r openssh, cache=TRUE}
openssh_version_history()
```

SQLite

```{r sqlite, cache=TRUE}
sqlite_version_history()
```

sendmail

```{r sendmail, cache=TRUE}
sendmail_version_history()
```
